Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-04 metrics.tex
Ready for now..

\subsection{Goodput}
We consider the goodput defined as the ratio of the useful delivered
information at the application layer and the total processing time. We focus
on the goodput considering only the coding process, i.e. we assume that
the application data has been properly generated before encoding and
also correctly post-processed after decoding. In this way, we define
the goodput for either an encoder or a decoder as follows:
%
\begin{align} \label{eq:goodput}
Goodput = \frac{gB}{T_{proc}} ~ [\mathrm{Bytes/s}]
\end{align}
%
In \eqref{eq:goodput}, $B$ and $g$ are the packet and generation size
as defined previously and both represented the data to be processed. For
goodput measurements, we are concerned in quantifying the processing time
for either encoding or decoding $g$ \ac{l.i.} packets. Thus, $T_{proc}$ is
the processing time required for this processing. In the next subsections, we
define two time bechmarks available in [\textbf{Chres repos here}].
The purpose of the benchmarks is to quantify the processing time for
any of the coding schemes considered in Section \ref{sec:schemes}.

@@

\subsection{Power and Energy Consumption}
In large-scale networks where several \ac{Raspi}s might be deployed,
both average power and energy per bit consumption of the devices are
relevant parameters that impact in the network performance for a given
coding scheme. The average power specifies the rate at which energy
consumed in the \ac{Raspi}, thus it provides information about the autonomy

\subsubsection{Average Power}
\subsubsection{Energy per Bit Consumption}

>>>>

\subsection{Goodput}
We consider the goodput defined as the ratio of the useful delivered
information at the application layer and the total processing time. We focus
on the goodput considering only the coding process, i.e. we assume that
the application data has been properly generated before encoding and
also correctly post-processed after decoding. In this way, we define
the goodput for either an encoder or a decoder as follows:
%
\begin{align} \label{eq:goodput}
R_{proc} = \frac{gB}{T_{proc}} ~ [\mathrm{Bytes/s}]
\end{align}
%
In \eqref{eq:goodput}, $B$ and $g$ are the packet and generation size
as defined previously and both represented the data to be processed. For
goodput measurements, we are concerned in quantifying the processing time
for either encoding or decoding $g$ \ac{l.i.} packets. Thus, $T_{proc}$ is
the processing time required for this processing. In the next subsections, we
define two time bechmarks available in [\textbf{Chres repos here}].
The purpose of the benchmarks is to quantify the processing time for
any of the coding schemes considered in Section \ref{sec:schemes}.

@@

\subsection{Energetic Expenditure}
In large-scale networks where several \ac{Raspi}s might be deployed,
both average power and energy per bit consumption of the devices are
relevant parameters that impact in the network performance for a given
coding scheme. Hence, we consider a study of these energy expenditure
parameters for the encoding and decoding. We define these metrics
and propose a setup to measure them.

The average power specifies the rate at which energy is
consumed in the \ac{Raspi}. Thus, for a given energy value in the device
battery without any external supplies, this metric permits to infer the amount
of time for which the \ac{Raspi} can operate autonomously before draining
out its battery. For the energy per bit consumption, it indicates how
much energy is expended to effectively transmit or receive 1 bit of bit
considering the encoding or decoding respectively. This energy is computed

For our energy measurement campaign, we automate the setup presented
in Fig. \ref{fig:measurement_setup} to sequentially run a series of
simulations for a given configuration of coding scheme and parameters,
to estimate the energy consumption in both of our \ac{Raspi}
models. A representative sketch of the setup is shown in the
computer monitor in Fig. \ref{fig:measurement_setup}. The figure presents
a \ac{Raspi} device whose power supply is an Agilent 66319D \ac{DC} source,
instead of its conventional chorded supply. The output of the measurements
are later sent to a workstation where the raw measurement data is processed.
The measured variable was the current consumed by the device for a fixed
5V supply from the source. To identify each experiment, we classified the
electrical current samples into two groups based on the magnitude. In our
measurements, the groups to be reported are the idle current $I_{idle}$
and the processing current $I_{proc}$. The former is the current the
\ac{Raspi} requires while in idle state, meaning that no processing
is being carried. The latter stands for the current needed during
the encoding or decoding processing of the packets. The measurements
where $I_{proc}$ is observed are made for a given configuration of
coding scheme with its parameters. Finally, each simulation was enumerated
to map the coding speed measurements with the corresponding energy
consumption.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.7\textwidth]{images/measurement_setup.eps}
\caption{Energy measurement setup}
\label{fig:measurement_setup}
\end{figure}

\subsubsection{Average Power Expenditure}
To extract the energy consumption of network coding, we subtracted the
idle energy consumption from the energy consumption used during simulations.

%
\begin{align} \label{eq:avg_current}
I_{avg} = \frac{1}{N_s}\sum_{k=1}^{N_s} I_{k}  ~[\mathrm{Amperes}]
\end{align}
%

%
\begin{align} \label{eq:avg_power}
P_{avg} = V_{supply}(I_{proc,avg} - I_{idle,avg}) ~[\mathrm{Watts}]
\end{align}
%
\subsubsection{Energy per Bit Consumption}
%
\begin{align} \label{eq:goodput}
E_b = P_{avg} T_{proc} = P_{avg} \times \frac{gB}{R_{proc}} ~[\mathrm{Joules/bit}]
\end{align}
%
